Conservation and losses of avian non-coding RNAs

### 2014-05-01 paper/manuscript.tex
Updated Acknowledgements.

Magnus Alm Rosenblad (Univ. of Gothenburg) for useful discussions.

We thank Fiona McCarthy (Mississippi State University) and Carl
Schmidt (University of Delaware) as well as Matt Schwartz (Harvard)
and Igor Ulitsky (Weizmann Institute of Science) for providing the
RNA-seq data as part of the Avian RNAseq consortium.

>>>>

Magnus Alm Rosenblad (Univ. of Gothenburg) and Eric Nawrocki (HHMI
Janelia Farm) for useful discussions.

We thank Fiona McCarthy (University of Arizona) and Carl
Schmidt (University of Delaware) as well as Matt Schwartz (Harvard)
and Igor Ulitsky (Weizmann Institute of Science) for providing the
RNA-seq data as part of the Avian RNAseq consortium.
